% Copyright 2014 Rob Myers
% License: http://creativecommons.org/licenses/by-sa/4.0/

\documentclass{beamer}
\input{theme.tex}

\usepackage[latin1]{inputenc}
\title{Ethereum Install Party!}
\author{Rob Myers\\http://robmyers.org}
\begin{document}

\maketitle{}

\begin{frame}
\textbf{Get the resources for this talk here:}
\newline{}
https://github.com/robmyers/ethereum-install-party
\end{frame}


\begin{frame}
\textbf{What Is Ethereum?}
\begin{itemize}
  \item{A distributed application platform}
  \item{A blockchain-based system (like Bitcoin)}
  \item{A trustless public ledger of state and agreements}
  \item{A store for arbitrary scripts and data}
  \item{An agoric computing system powered by ``Ether''}
\end{itemize}
\end{frame}


\begin{frame}
\textbf{What Can We Use Ethereum for?}
\begin{itemize}
  \item{Smart contracts}
  \item{Smart property, digital and physical}
  \item{Distributed Autonomous Organizations (DAOs)}
  \item{AltCoins, Crypto-Equity, anything Bitcoin or NXT can do}
  \item{Things we haven't thought of yet}
\end{itemize}
\end{frame}


\begin{frame}
\textbf{How Is Ethereum Implemented?}
\begin{itemize}
  \item{c++ - cpp-ethereum, AlethZero}
  \item{go - go-ethereum, Ethereal}
  \item{python - pyEthereum}
  \item{java - ethereumj}
  \item{javascript - UI bindings, node.js}
\end{itemize}
\end{frame}


\begin{frame}
\textbf{How Does Ethereum Work?}
\begin{itemize}
  \item{Addresses}
  \item{Contracts}
  \item{Storage}
  \item{Transactions}
  \item{Ether}
\end{itemize}
\end{frame}


\begin{frame}
\textbf{OK, Let's Install Ethereum!}
\newline{} \newline{}
Mac \& Windows, grab the installer:
\newline{}
https://github.com/ethereum/cpp-ethereum/releases
\newline{} \newline{}
GNU/Linux, look here:
\newline{}
https://github.com/ethereum/cpp-ethereum/wiki
\end{frame}


\begin{frame}
\textbf{Let's Run AlethZero}
\begin{itemize}
  \item{Start AlethZero}
  \item{Connect to peer}
  \item{Enable mining (transactions cost Ether!)}
\end{itemize}
\end{frame}


\begin{frame}
\textbf{Let's Try Some Contracts!}
\begin{itemize}
  \item{GavCoin - http://gavwood.com/gavcoin.html}
  \item{PRODOUG - https://androlo.github.io/andreasweb/DAO.html}
\end{itemize}
\end{frame}


\begin{frame}
\textbf{How Do We Write Ethereum Contracts?}
\newline{}
QML or Web-app-style
\newline{}
For Web-app-style:
\begin{itemize}
  \item{User Interface (View): HTML}
  \item{Communication (Controller): JavaScript}
  \item{Data Manipulation and storage (Model): lll/Serpent/Mutan}
\end{itemize}
\end{frame}


\begin{frame}
\textbf{More Information}
\begin{itemize}
  \item{https://www.ethereum.org/}
  \item{https://github.com/ethereum/wiki/wiki/\%5BEnglish\%5D-White-Paper}
  \item{http://www.slideshare.net/ethereum/the-ethereum-experience}
  \item{https://www.youtube.com/user/EtherCasts}
  \item{http://forum.ethereum.org/}
\end{itemize}
\end{frame}

\end{document}
